---
title: Module's Programming Assignment
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment = '')
library(dplyr)
library(tidyr)
library(readr)
library(readxl)
```
<style>
  body {
    text-align: justify}
</style>

## 1.

Use the readr package to read the daily_SPEC_2014.csv.bz2 data file in to R. This file
contains daily levels of fine particulate matter (PM2.5) chemical constituents across the
United States. The data are measured at a network of federal, state, and local monitors and
assembled by the EPA.

In this dataset, the "Sample.Value" column provides the level of the indicated chemical
constituent and the "Parameter.Name" column provides the name of the chemical constituent.
The combination of a "State.Code", a "County.Code", and a "Site.Num", uniquely identifies a
monitoring site (the location of which is provided by the "Latitude" and "Longitude"
columns).

For all of the questions below, you can ignore the missing values in the dataset, so when
taking averages, just remove the missing values before taking the average (i.e. you can use
na.rm = TRUE in the mean() function)

What is average Arithmetic.Mean for “Bromine PM2.5 LC” in the state of Wisconsin in this
dataset?

<u>answer</u>

```{r a1}
data <- read_csv('data/daily_SPEC_2014.csv.bz2',progress = FALSE)
names(data) ## take a look at the column names
names(data) <- gsub('\\s','.',names(data))
names(data)[3] <- "Site.Number"
sapply(data,class) ## to see the class of each column
for (i in 1:3) data[,i] <- as.numeric(unlist(data[,i]))
rm(i)
data %>% filter(Parameter.Name == "Bromine PM2.5 LC",State.Name == "Wisconsin") %>% 
  summarise(average_mean = mean(Arithmetic.Mean,na.rm = TRUE))
```

## 2.

Calculate the average of each chemical constituent across all states, monitoring sites and all time 
points.

Which constituent Parameter.Name has the highest average level?

<u>answer</u>

```{r a2}
data %>% group_by(State.Name,Site.Number,Date.Local,Parameter.Name) %>% 
  summarise(Average.Level = mean(Arithmetic.Mean,na.rm = TRUE)) %>% arrange(desc(Average.Level)) %>%
  head(1)
```

## 3.

Which monitoring site has the highest average level of “Sulfate PM2.5 LC” across all time?

Indicate the state code, county code, and site number.

<u>answer</u>

```{r a3}
data %>% group_by(State.Code,County.Code,Site.Number) %>% 
  filter(Parameter.Name == "Sulfate PM2.5 LC") %>% 
  summarise(Average.Level = mean(Arithmetic.Mean,na.rm = TRUE)) %>% arrange(desc(Average.Level)) %>%
  head(1)
```

## 4.

What is the absolute difference in the average levels of “EC PM2.5 LC TOR” between the states California
and Arizona, across all time and all monitoring sites?

<u>answer</u>

```{r a4}
data %>% filter(Parameter.Name == "EC PM2.5 LC TOR",State.Name %in% c("California","Arizona")) %>% 
  group_by(State.Name) %>% summarise(Average.Levels = mean(Arithmetic.Mean,na.rm = TRUE)) %>% 
  ungroup %>%
  transmute(Abs.Difference = abs(max(Average.Levels) - min(Average.Levels))) %>% head(1)
```

## 5.

What is the median level of “OC PM2.5 LC TOR” in the western United States, across all time? Define
western as any monitoring location that has a Longitude LESS THAN -100.

<u>answer</u>

```{r a5}
data %>% filter(Parameter.Name == "OC PM2.5 LC TOR",Longitude < -100) %>% group_by(Parameter.Name) %>% 
  summarise(Median.Level = median(Arithmetic.Mean,na.rm = TRUE)) 
```

## 6.

Use the readxl package to read the file aqs_sites.xlsx into R (you may need to install the package
first). This file contains metadata about each of the monitoring sites in the EPA’s monitoring system.
In particular, the "Land Use" and "Location Setting" variables contain information about what kinds of 
areas the monitors are located in (i.e. “residential” vs. “forest”).

How many monitoring sites are labelled as both RESIDENTIAL for "Land Use" and SUBURBAN for "Location 
Setting"?

<u>answer</u>

```{r a6}
data1 <- read_excel('data/aqs_sites.xlsx')
names(data1) <- gsub("\\s",".",names(data1))
data1 %>% filter(Land.Use == "RESIDENTIAL",Location.Setting == "SUBURBAN") %>% nrow
```

## 7.

What is the median level of “EC PM2.5 LC TOR” amongst monitoring sites that are labelled as both
“RESIDENTIAL” and “SUBURBAN” in the eastern U.S., where eastern is defined as Longitude greater than or
equal to -100?

<u>answer</u>

```{r a7}
joined <- left_join(data,data1,by = c("State.Code","County.Code","Site.Number"))
joined %>% filter(Land.Use == "RESIDENTIAL",Location.Setting == "SUBURBAN",Longitude.x >= -100,
                  Parameter.Name == "EC PM2.5 LC TOR") %>% group_by(Parameter.Name) %>% 
  summarise(Median.Level = median(Arithmetic.Mean,na.rm = TRUE))
```

## 8.

Amongst monitoring sites that are labeled as COMMERCIAL for “Land Use”, which month of the year has the 
highest average levels of “Sulfate PM2.5 LC”?

<u>answer</u>

```{r a8}
joined %>% filter(Land.Use == "COMMERCIAL",Parameter.Name == "Sulfate PM2.5 LC") %>% 
  mutate(Date.Local = months(Date.Local,abbreviate = FALSE)) %>%
  group_by(Date.Local) %>% summarise(Mean.Level = mean(Arithmetic.Mean,na.rm = TRUE)) %>% 
  arrange(desc(Mean.Level))
```

## 9.

Take a look at the data for the monitoring site identified by State Code 6, County Code 65, and Site 
Number 8001 (this monitor is in California). At this monitor, for how many days is the sum of “Sulfate 
PM2.5 LC” and “Total Nitrate PM2.5 LC” greater than 10?

<u>answer</u>

```{r a9}
rm(joined)
data %>% filter(State.Code == 6,County.Code == 65,Site.Number == 8001,
                Parameter.Name %in% c("Sulfate PM2.5 LC","Total Nitrate PM2.5 LC")) %>% 
  select(Date.Local,Parameter.Name,Arithmetic.Mean) %>% group_by(Date.Local,Parameter.Name) %>% 
  summarise(Average.Level = mean(Arithmetic.Mean,na.rm = TRUE)) %>% group_by(Date.Local) %>% 
  spread(key = Parameter.Name,value = Average.Level) %>% mutate(Total = `Sulfate PM2.5 LC` + 
        `Total Nitrate PM2.5 LC`) %>% filter(Total > 10) %>% nrow
```

## 10.

Which monitoring site in the dataset has the highest correlation between “Sulfate PM2.5 LC” and “Total 
Nitrate PM2.5 LC” across all dates? Identify the monitoring site by it’s State, County, and Site Number 
code.

<u>answer</u>

```{r a10}
data %>% filter(Parameter.Name %in% c("Sulfate PM2.5 LC","Total Nitrate PM2.5 LC")) %>% 
  group_by(State.Code,County.Code,Site.Number,Parameter.Name,Date.Local) %>% 
  summarise(Average.Level = mean(Arithmetic.Mean,na.rm = TRUE)) %>% spread(key = Parameter.Name,value =
  Average.Level) %>% group_by(State.Code,County.Code,Site.Number) %>%
  summarise(Cor = cor(`Sulfate PM2.5 LC`,`Total Nitrate PM2.5 LC`)) %>% arrange(desc(Cor))
rm(data)
rm(data1)
```