---
title: "Fars Package Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bundle_Of_Functions_For_Exploring_Fatality_Census_Project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fars)
```


# Helper Functions To Explore The Fatality Cencus Datasets

This packages aims to produce simple graphics to show the accidents in US territory. In this 
*vignette* we are going to give simple examples of how to use the functions of the package, for 
this purpose we have stored three data sets found in
`r system.file("exdata",package = "Highway.Fatality.Census.Project")`
, we will use _accident_2013_, there are two other data files in 
`r system.file("exdata",pachage = "fars")`.
We provide some description but with some examples, you are free to experiment on your own.

## The `make_filename` function

Creates the filename by entering the year as input. 

```{r 1}
filename <- make_filename(2013)
basename(filename)
```

## The `fars_read` function

The _fars_read_ will use as input the filename string from _make_filename_.

```{r 2}
read_data <- fars_read(filename)
read_data
```

## The `fars_read_years` function

This functions goes further and use the both functions (_make_filename_ and _fars_read_) 
to generate a list.

```{r 3}
fars_read_years(2013)
```

## The `fars_summarize_years` function

This functions prints a summary of a vector of years.

```{r 4,eval = FALSE}
fars_summarize_years(c(2013,2014))
```
## The `fars_map_state` function

Plot a Graphic of each State of US.

```{r 5}
fars_map_state(34,2013)
```

## Dependencies

* dplyr
* magrittr
* tidyr
* rlang
* graphics
* maps
